When are Fuzzy Extractors Possible?

### 2015-02-09 info-bounds/FuzzyExtPossibility.tex
revised proof leveled hashing

\begin{definition}
\label{def:fuzzy min-ent}
The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
\[
\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
\]
\end{definition}
\noindent
Fuzzy min-entropy is a necessary condition for security.  It measures the advantage provided to the adversary by allowing them to run the $\rep$ functionality.  Thus, the fuzzy min-entropy is the ideal security that any fuzzy extractor should be compared against.
\begin{proposition}~(proof in \apref{sec:proof fuzz necessary})
\label{prop:fuzz necessary}
Let $W$ be a distribution  over $(\mathcal{M}, \dis)$ with $\Hfuzz(W) =m$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, W, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$.  Then 
\[
\epsilon\ge 2^{-m}-\delta -2^{-\kappa}.
\]
In particular, for security parameter $n$, if $m = \Theta(\log n), \delta = \ngl(n), \kappa = \omega(\log n)$, then $\epsilon  = 1/\poly(n)$.
%If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
% with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
\end{proposition}

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
The proof of \propref{prop:fuzz necessary} is not specific to the fuzzy extractor setting, it also applies to computational and interactive definitions.  There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
Our goal is to provide a superlogarithmic length key whenever a distribution has superlogarithmic fuzzy min-entropy.

@@

\noindent
Fuzzy min-entropy obeys a chain rule:
\begin{lemma}~(proof in \apref{sec:proof fuzz necessary})
\label{lem:chain rule fuzz}
$\Hfav(W|P) \ge \Hfuzz(W) - H_0(P)$.
\end{lemma}

@@

%\begin{corollary}
%\label{cor:no fuzz for dist}
%Let $\mathcal{W}$ be a family of distributions.  Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.  If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
%\end{corollary}
%
%Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
\section{Fuzzy min-entropy}
\label{sec:proof fuzz necessary}
\begin{proof}[Proof of \propref{prop:fuzz necessary}]
Let $W$ be a distribution where $\Hfuzz(W) = m$.  This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] = 2^{-m}$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $r, p$.
\item If $\rep(w', p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
Clearly, $\Pr[D(\Key, P) = 1]\geq 2^{-m} - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus,
\[
\sd((R, P), (U_\kappa, P)) \ge \delta^D((R, P), (U_\kappa, P))\geq 2^{-m} -\delta -2^{-\kappa}.
\]
\end{proof}

@@

\paragraph{Security:}
We now argue security of the construction.  First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.  Then 
\begin{align}
\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\nonumber\\
&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)
\end{align}
For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$

We now show that the fuzzy min-entropy conditioned on the level information is proportional to $\beta_{t, i}$.  Let $I$ be the random variable of the level information.
\begin{claim}
$\Hoo(W | I=i ) -\log \beta_{t, i} \ge \Hfuzz(W | I =i ) \ge \Hoo(W | I =i ) -\log \beta_{t, i}-1$.
\end{claim}
\begin{proof}
We show the left inequality first.
\begin{align*}
\Hfuzz(W|I=i) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \Pr[W=w | I=i]\right) \right)\\
&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
&= (m+i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
&=(m+i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-(m+i)}\right) \right)\\
&=(m+i)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)\\
&= m+i-\log \beta_{t, i}.
\end{align*}
We now show the right inequality.
\end{proof}

\bnote{new outline to proof. proof to come}
\begin{enumerate}
\item show chain rule for fuzzy min-entropy
\item show that fuzzy min-entropy conditioned on i is related to $\beta_{t, i}$.
\item show that releasing the sketch only gives delta more than necessary.
\end{enumerate}
\noindent
\textbf{Ideal Adversary with access to Level Information:} To aid in the argument in security, we show the level information on its own is not too harmful.  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.

Let $I$ be the random variable describing the level.  Since there are at most $n$ outcomes for the level when $1_{\text{low}} =0$, we have that \[\Hav( W | I \wedge 1_{\text{low}}=0) \ge \Hoo(W) -\log n.\]

In the standard secure sketch game, to maximize probability of predicting $w$, the adversary supplies the $w'$ with the most nearby probability mass.  With the additional information about the probability of $w$, the adversary should supply $w'$ with the most nearby probability in the correct probability level.  That is, the adversary's best guess is:
\[
w^*= \argmax_{w' \in \mathcal{M}}\sum_{w\in W | \Pr[W=w]\in L_i\wedge \dis(w, w')}\Pr[W=w].
\] 
The success of this adversary is at most $2^{-i}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at most $2^{-i}$.  There are $n$ outcomes for $i$. The overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).  That is, 
\begin{align}
\expe_{i | m\le i \le m+n}2^{-i}\beta_{t,i}%&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W|  w\in L_i \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
%&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
&\ge n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
\end{align}
\textbf{Security:}
%We just saw that an adversary that learns $L_i$ performs at most a factor of $n$ better than an adversary without this information.

Let $L_I$ denote the random variable denoting the probability of $\Pr[W=w]$.
All the dependence between $W$ and $K$ is contained in $L_I$.   That is, $\Hav(W | K_I , L_I) = \Hav(W | L_I)$. Let $Y_I$ denote the outcome of the hash function.  We now consider the remaining average min-entropy when $1_{\text{low}} = 0$:
\begin{align*}
\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &= \Hav(W | L_I , K_I, Y_I \wedge 1_{\text{low}}=0)\\
&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | K_i , Y_i, i)}\right)\right)\\
&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | Y_i, i)}\right)\right)\\
&\ge -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(\frac{(\beta_{t, i}-1)}{\delta}2^{-\Hav(W | i)}\right)\right)\\
&= -\log \left(\frac{1}{\delta}\left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i)}\right)\right)\right)\\
&= -\log \left(\frac{2}{\delta} \left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i+1)}\right)\right)\right)\\
&= -\log \left(\frac{2n}{\delta} 2^{-\Hfuzz(W)}\right)\\
\end{align*}
Where the first inequality proceeds by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}
\begin{align*}
\max_{w\in W | 2^{-(m+n)}< \Pr[W=w]}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(\frac{2^{-i}*\beta_{t,i}}{\delta}\right)\\
&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot \beta_{t,i}\right)}{2\delta}\\
%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*\beta_{t,i}\right)
%\end{align*}
%Now consider This allows us to conclude that 
%\begin{align*}
%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
\end{align*}
Where the last line follows by Equation~\eqref{eq:link fuzz 3}.
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) &\ge -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
&\ge -\log \min\{2^{-m}, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
\end{align*}
Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
\end{proof}

>>>>

\begin{definition}
\label{def:fuzzy min-ent}
The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
\[
\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
\]
\end{definition}
\noindent
Fuzzy min-entropy is a necessary condition for security.  It measures the advantage provided to the adversary by allowing them to run the $\rep$ functionality.  Thus, the fuzzy min-entropy is the ideal security that any fuzzy extractor should be compared against.  All proofs for statements in this section can be found in \apref{sec:proof fuzz necessary}.
\begin{proposition}
\label{prop:fuzz necessary}
Let $W$ be a distribution  over $(\mathcal{M}, \dis)$ with $\Hfuzz(W) =m$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, W, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$.  Then 
\[
\epsilon\ge 2^{-m}-\delta -2^{-\kappa}.
\]
In particular, for security parameter $n$, if $m = \Theta(\log n), \delta = \ngl(n), \kappa = \omega(\log n)$, then $\epsilon  = 1/\poly(n)$.
%If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
% with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
\end{proposition}

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
The proof of \propref{prop:fuzz necessary} is not specific to the fuzzy extractor setting, it also applies to computational and interactive definitions.  There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
Our goal is to provide a superlogarithmic length key whenever a distribution has superlogarithmic fuzzy min-entropy. 
Fuzzy min-entropy obeys some natural entropy properties:
\begin{lemma}
\label{lem:conditional fuzz rule}
$\Hfuzz(W|P=p) \ge \Hfuzz(W) + \log \Pr[P=p]$.
\end{lemma}

@@

\begin{lemma}
\label{lem:chain rule fuzz}
$\Hfav(W|P) \ge \Hfuzz(W) - H_0(P)$.
\end{lemma}

@@

%\begin{corollary}
%\label{cor:no fuzz for dist}
%Let $\mathcal{W}$ be a family of distributions.  Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.  If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
%\end{corollary}
%
%Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
\section{Fuzzy min-entropy}
\label{sec:proof fuzz necessary}
\begin{proof}[Proof of \propref{prop:fuzz necessary}]
Let $W$ be a distribution where $\Hfuzz(W) = m$.  This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] = 2^{-m}$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $r, p$.
\item If $\rep(w', p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
Clearly, $\Pr[D(\Key, P) = 1]\geq 2^{-m} - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus,
\[
\sd((R, P), (U_\kappa, P)) \ge \delta^D((R, P), (U_\kappa, P))\geq 2^{-m} -\delta -2^{-\kappa}.
\]
\end{proof}
\begin{proof}[Proof of \lemref{lem:conditional fuzz rule}]
\begin{align*}
\Hfuzz(W | P=p) &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \Pr[W=w | P=p] \right)\\
 &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w \wedge P=p]}{\Pr[P=p]} \right)\\
 &\ge -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
 &\ge -\log \left(\max_{w'}  \sum_{w\in W| \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
 &= \Hfuzz(W) - \log \frac{1}{\Pr[P=p]}.
\end{align*}
\end{proof}

@@

\paragraph{Security:}
We now argue security of the construction.  First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.  Then 
\begin{align}
\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\nonumber\\
&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)
\end{align}
For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $I$ be the random variable of the level information (in what follows, $I$ ranges over $m\le i \le m+n$, where possible we omit this for notation clarity).

\begin{align}
\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}}=0 \wedge I=i}) \right)\nonumber\\
&=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \mathcal{K}_i \wedge F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge I=i)}\right)\nonumber\\
&=-\log \left( \expe_{i\in I} 2^{-\Hav(W |  F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge I=i)}\right)\nonumber\\
&\ge-\log \left( \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1) +\log \delta)}\right)\nonumber\\
&\ge-\log \left(\frac{1}{\delta} \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1))}\right)\nonumber\\
&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1))}\right) - \log \frac{1}{\delta}\nonumber\\
&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}))}\right) - \log \frac{1}{\delta}\label{eq:fuzzy ball size}
\end{align}

\noindent
We now show that the fuzzy min-entropy conditioned on the level information is proportional to $\beta_{t, i}$.  
\begin{claim}
\label{cl:fuzz proportional beta}
\[\Hoo(W | 1_{\text{low}} =0 \wedge J=j ) -\log \beta_{t, i} \ge \Hfuzz(W | J=j \wedge 1_{\text{low}}=0)+1.\]
\end{claim}
\begin{proof}
For convenience denote by $J=j$ the random variable $1_{\text{low}}=0 \wedge I=i$. 
\begin{align*}
\Hfuzz(W|J=j) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \Pr[W=w | J=j]\right) \right)\\
&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \min_{w^*\in W=w| J=j}\Pr[W=w^* | J=j]\right) \right)\\
&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \max_{w^*\in W=w| J=j}\Pr[W=w^* | J=j]\right) \right)+1\\
&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-\Hoo(W|J=j)}\right) \right)+1\\
&= \Hoo(W|J=j)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 1\right) \right)+1\\
&=\Hoo(W|J=j)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)+1\\
&=\Hoo(W|J=j)+1-\log \beta_{t, i}.
\end{align*}
Where the third line follows by \clref{cl:nearly flat after conditioning}, which follows.  This completes the proof of \clref{cl:fuzz proportional beta}.
\end{proof}

\begin{claim}
\label{cl:nearly flat after conditioning}
Let $W$ be a distribution and let $S\subset W$ such that for all $w_1, w_2 \in S$, $\Pr[W=w_1]\ge \Pr[W=w_2]$.  Let $J$ be as above, then for all $w_1, w_2 \in (S \wedge W|J=j )$, $\Pr[W=w_1 | J=j]\ge \Pr[W=w_2 | J=j]/2$.
\end{claim}
\begin{proof}
\begin{align*}
\Pr[W=w_1 | J=j] &=&\frac{\Pr[W=w_1\wedge J=j] }{\Pr[J=j]}
&=& \frac{\Pr[W=w_1]}{\Pr[J=j]}\\
&\ge& \frac{\Pr[W=w_2]}{2 \Pr[J=j]}
&=& \frac{\Pr[W=w_2 \wedge J=j]}{2\Pr[J=j]}\\
&=&\frac{\Pr[W=w_2]}{2}.
\end{align*}
Where the first and last equality follow by Bayes' rule.  The second and fourth equality follow by noting that $\Pr[W=w \wedge J=j] = \Pr[W=w]$ for all $w\in L_i$.  The inequality proceeds by assumption.  This completes the proof of \clref{cl:nearly flat after conditioning}.
\end{proof}

\noindent 
We now return to the proof of \lemref{lem:flat hashing}. Together Equation \ref{eq:fuzzy ball size} and \clref{cl:fuzz proportional beta} yield:
\begin{align*}
\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}}=0)-1}\right) -\log \frac{1}{\delta} \\
&=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}} =0)}\right) -1- \log \frac{1}{\delta} \\
&=\Hfav(W | I \wedge 1_{\text{low}}=0)-1- \log \frac{1}{\delta} \\
&\ge\Hfuzz(W | 1_{\text{low}}=0)-1-\log n -\log \frac{1}{\delta}\\
&\ge\Hfuzz(W)-1-\log n -\log \frac{1}{\delta} - \log (1-2^{-m})
\end{align*}
Where the second-to-last line follows by \lemref{lem:chain rule fuzz}.  The last line follows by \lemref{lem:conditional fuzz rule} and by noting that $\Pr[1_{\text{low}}=0] \ge 1/(1-2^{-m})$.
Returning to equation \ref{eq:min-entropy} one has:
\begin{align*}
\Hav(W | \sketch(W)) &\ge -\log\left( 2^{-m} + (1-2^{-m}) 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)\\
&\ge -\log \left(2^{-m}+2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta-2\log (1-2^{-m}) )}\right)\\
&\ge -\log \min\{2^{-m}, 2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta-2\log (1-2^{-m}) )}\}-1\\
&\ge \Hfuzz(W) - 2- \log n - \log 1/\delta  -2\log (1-2^{-m}) \\
&\ge \Hfuzz(W) - 3- \log n - \log 1/\delta
\end{align*}
Where the fourth line follows from the third because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$, then $\log (1-2^{-m}) \le 1$ and if $m<1$ the entire bound is vacuous as $\Hfuzz(W) < 1$.
\end{proof}
